### 2020-02-17 Article.tex
Pequeño update

The excess $ex(G)$ of an hypergraph $G$ is the number
\[
ex(G)= \big(\sum_{i=1}^{t} (a_i-1)|E_i(G)|\big) - |V(G)|.  
\] 
That is, the excess of $G$ is its "weighted number of edges"
minus its number of vertices. Here the "weighted number of edges"
in $G$ the sum of the weight of all its edges, where the
weight of an edge is its size minus one.

@@

Our main tool for computing probabilities will be
the following multivariate version of Brun's Sieve 
CITA REQUERIDA

\begin{theorem}
	Fix $k\in \N$. For each 
	$n\in \N$, let $X_{1,n},\dots, X_{k,n}$ be non-negative
	random integer variables over the same
	probability space. Let $\lambda_1,\dots,\lambda_l$ 
	be real numbers. Suppose that for any $r_1,\dots,r_l \in \N$
	\[ 
	\Ln \mathrm{E}\big[
	\prod_{i=1}^{k} (X_{i,n})_{r_i} \big]
	= \prod_{i=1}^{k} \frac{\lambda_i}{r_i !}.	
	\]
	Then the $X_{1,n},\dots,X_{k,n}$ converge in distribution to
	independent Poisson variables with means $\lambda_1,\dots,\lambda_k$ 
	respectively. 
\end{theorem}

@@

\begin{theorem} 
	The following are satisfied:
	\begin{itemize}
		\item[(1)] Let $r\in \N$ and let $\mathcal{T}$ be a
		$k$-equivalence class for trees with radii at most $r$.
		Then $\mathrm{Pr}[r,\mathcal{T}]$ exists and is an expression
		in $\Lambda$.
		\item[(2)] Let $\overbar{w}\in \N*$ be a list of different fixed 
		vertices, and let $\phi[\overbar{x}]\in FO[\sigma]$ be an open sentence
		(i.e. with no bounded variables) such that $\overbar{x}$ and $\overbar{w}$
		have the same size. Let $=v_1,\dots,v_k \in \N$ be another 
		list of different vertices that are contained in $\overbar{w}$.
		Let $r_1,\dots,r_k \in \N$ and let $\mathcal{T}_1,\dots \mathcal{T}_k$
		be $k$-equivalence classes for trees such that
		each $\mathcal{T}_i$ has radii bounded by $r_i$. Then
		\[
		\Ln \mathrm{Pr}\big( \bigwedge_{i=1}^k 
		T_{n,i}=T_n(v_i,\overbar{w};r_i) \text{ is a tree and } 
		(T_{n,i},v_i)\in \mathcal{T}_i \, | \, \sigma(\overbar{w})
		\big)= \prod_{i=1}^k \mathrm{Pr}[r_i,\mathcal{T}_i]. \]		
	\end{itemize}
	\begin{proof}
		Let $R$ be an upper bound of the radius of $r$ and the 
		$r_i$'s	in the statement. 
		We will prove (1) and (2) together by induction on $R$. \par
		Assume $R=0$. We start by showing that (1) holds. Recall that
		all trees with radius zero are $k$-equivalent. Thus, if
		$\mathcal{T}$ is the unique $k$-equivalence class of trees
		with radius zero
		and $v\in \N$ is a fixed vertex, then
		 \[
		 \mathrm{Pr}[0;\mathcal{T}] = \Ln \mathrm{Pr}\big( 
		 T:=N^{G_n}(v;0) \text{ is a tree, and } (T,v)\in \mathcal{T} \big)
		 =1, 
		 \]
		Indeed, $N^{G_n}(v;0)$ consists of a single vertex for all $n\geq v$,
		and the above equation follows. The expression $1$ belongs to 
		$\Lambda$, so (1) holds. \par
		The case of (2) is analogous. As $R=0$, then $\mathcal{T}_1=\dots=
		\mathcal{T}_k$ are the unique $k$-equivalence class of trees with
		radius zero. Then, given $\sigma, \overbar{w}, v_1,\dots, v_k$ as
		in the statement,
		\[\Ln \mathrm{Pr}\big( \bigwedge_{i=1}^k 
		T_{n,i}=T_n(v_i,\overbar{w};0) \text{ is a tree and } 
		(T_{n,i},v_i)\in \mathcal{T}_i \, | \, \sigma(\overbar{w})
		\big)=1. \]	
		Because of (1), $\mathrm{Pr}[0,\mathcal{T}_i]=1$ for all $i$'s, 
		and (2) holds. \par
		Now let $R>0$ and assume that both (1) and (2) hold for all 
		lesser values of $R$.

>>>>

The excess $ex(G)$ of an hypergraph $G$ is the number
\[
ex(G)= \big(\sum_{i=1}^{t} (a_i-1)|E_i(G)|\big) - |V(G)|.  
\] 
That is, the excess of $G$ is its "weighted number of edges"
minus its number of vertices. \par

@@

Our main tool for computing probabilities will be
the following multivariate version of Brun's Sieve (
Theorem 1.23, \cite{bollobas2001random}).

\begin{theorem}
	Fix $k\in \N$. For each 
	$n\in \N$, let $X_{n,1},\dots, X_{n,k}$ be non-negative
	random integer variables over the same
	probability space. Let $\lambda_1,\dots,\lambda_l$ 
	be real numbers. Suppose that for any $r_1,\dots,r_l \in \N$
	\[ 
	\Ln \mathrm{E}\big[
	\prod_{i=1}^{k} (X_{n,i})_{r_i} \big]
	= \prod_{i=1}^{k} \frac{\lambda_i}{r_i !}.	
	\]
	Then the $X_{n,1},\dots,X_{n,k}$ converge in distribution to
	independent Poisson variables with means $\lambda_1,\dots,\lambda_k$ 
	respectively. 
\end{theorem}

@@

\begin{theorem} 
	The following are satisfied:
	\begin{itemize}
		\item[(1)] Let $r\in \N$ and let $\mathcal{T}$ be a
		$k$-equivalence class for trees with radii at most $r$.
		Then $\mathrm{Pr}[r,\mathcal{T}]$ exists and is an expression
		in $\Lambda$.
		\item[(2)] Let $\overbar{w}\in \N*$ be a list of different fixed 
		vertices, and let $\phi[\overbar{x}]\in FO[\sigma]$ be an open sentence
		(i.e. with no bounded variables) such that $\overbar{x}$ and $\overbar{w}$
		have the same size. Let $=v_1,\dots,v_k \in \N$ be another 
		list of different vertices that are contained in $\overbar{w}$.
		Let $r_1,\dots,r_k \in \N$ and let $\mathcal{T}_1,\dots \mathcal{T}_k$
		be $k$-equivalence classes for trees such that
		each $\mathcal{T}_i$ has radii bounded by $r_i$. Then
		\[
		\Ln \mathrm{Pr}\big( \bigwedge_{i=1}^k 
		T_{n,i}=T_n(v_i,\overbar{w};r_i) \text{ is a tree and } 
		(T_{n,i},v_i)\in \mathcal{T}_i \, | \, \sigma(\overbar{w})
		\big)= \prod_{i=1}^k \mathrm{Pr}[r_i,\mathcal{T}_i]. \]		
	\end{itemize}
	\begin{proof}
		Let $R$ be an upper bound of the radius of $r$ and the 
		$r_i$'s	in the statement. 
		We will prove (1) and (2) together by induction on $R$. \par
		Assume $R=0$. We start by showing that (1) holds. Recall that
		all trees with radius zero are $k$-equivalent. Thus, if
		$\mathcal{T}$ is the unique $k$-equivalence class of trees
		with radius zero
		and $v\in \N$ is a fixed vertex, then
		 \[
		 \mathrm{Pr}[0;\mathcal{T}] = \Ln \mathrm{Pr}\big( 
		 T:=N^{G_n}(v;0) \text{ is a tree, and } (T,v)\in \mathcal{T} \big)
		 =1, 
		 \]
		Indeed, $N^{G_n}(v;0)$ consists of a single vertex for all $n\geq v$,
		and the above equation follows. The expression $1$ belongs to 
		$\Lambda$, so (1) holds. \par
		The case of (2) is analogous. As $R=0$, then $\mathcal{T}_1=\dots=
		\mathcal{T}_k$ are the unique $k$-equivalence class of trees with
		radius zero. Then, given $\sigma, \overbar{w}, v_1,\dots, v_k$ as
		in the statement,
		\[\Ln \mathrm{Pr}\big( \bigwedge_{i=1}^k 
		T_{n,i}=T_n(v_i,\overbar{w};0) \text{ is a tree and } 
		(T_{n,i},v_i)\in \mathcal{T}_i \, | \, \sigma(\overbar{w})
		\big)=1. \]	
		Because of (1), $\mathrm{Pr}[0,\mathcal{T}_i]=1$ for all $i$'s, 
		and (2) holds. \par
		Now let $R>0$ and assume that both (1) and (2) hold for all 
		lesser values of $R$.  \par
